# Exploratory Analysis 7/10 - First looks

### Reading in original data

```{r}
library(openxlsx) 
library(ggplot2)
library(ggrepel)
library(ggbreak) 
library(patchwork)
library(dplyr)
library(stringr)
library(lubridate)
library(readxl)
library(gtable)
library(gridExtra)



file_path <- "C:/Users/24chi/Desktop/OffshoreWind/DA_Classifications_Final.xlsx"

classData <- read_excel(file_path, sheet = 1) #Grabbing the data from excel
metaData <- read_excel(file_path, sheet = 2) #Grabbing the data from excel

classData$prj <- substr(classData$Code,1,3)
classData$comit <- as.numeric(substr(classData$Code,4,4))

classData$date <- metaData$prjDate[match(classData$prj, metaData$prjCode)]
classData$date <- as.Date(classData$date, format = "%m/%d/%Y")


widerCats <- list(c("MarineMams", "Turts", "Birds", "Bats", "Fish"),
  c("Benthic", "WaterQ", "AcouBelow", "EssFishHabs", "CoastalHabs", "WetLands"),
  c("RecComFisheries","VesselNav", "PubHealth"),
  c("CultArcheo" , "SocioEcon", "EnviroJustice","RecTourism"),
  c("Visual","AcouAbove", "FAA-DOD", "AirQ", "Other"))

widerCatsName <- c("Animals", "BenthicQuality", "Boats", "Human", "Air")

for (i in c(1:5)){
  classData[widerCatsName[i]] <- sapply(strsplit(classData$Prot, ",\\s*"), function(tags) any(tags %in% widerCats[[i]]))
}
classData$widerCatsall <- paste0(
  ifelse(classData$Animals, 'Animals, ', ''),
  ifelse(classData$BenthicQuality, 'BenthicQuality, ', ''), 
  ifelse(classData$Boats, 'Boats, ', ''), 
  ifelse(classData$Human, 'Human, ', ''), 
  ifelse(classData$Air, 'Air, ', ''))


```

Row Counting and plotting function

```{r}
RowCounts <- function(ClassData, Title, bin = NULL, mode = 'Doc') {
  lineCounts <- sort(table(ClassData$prj))
  
  
  
  count_df <- data.frame(Prj = names(lineCounts), Count = as.vector(lineCounts))
  count_df$date <- metaData$prjDate[match(count_df$Prj, metaData$prjCode)]
  count_df$dateSAP <- metaData$SAPprjDate[match(count_df$Prj, metaData$prjCode)]
  count_df$Dev <- metaData$Developer[match(count_df$Prj, metaData$prjCode)]
  count_df$Doc <- metaData$DocType[match(count_df$Prj, metaData$prjCode)]
  count_df$Consult <- metaData$Consultantcy[match(count_df$Prj, metaData$prjCode)]
  prjNames <- unique(classData$prj)
  for (i in prjNames){
    if (!(i %in% as.vector(count_df$Prj))){
      count_df <- rbind(count_df, data.frame(
                            Prj = i, 
                            Count = 0, 
                            date = metaData$prjDate[match(i, metaData$prjCode)],
                            dateSAP = metaData$SAPprjDate[match(i, metaData$prjCode)],
                            Dev = metaData$Developer[match(i, metaData$prjCode)], 
                            Doc = metaData$DocType[match(i, metaData$prjCode)],
                            Consult = metaData$Consultantcy[match(i, metaData$prjCode)]))
    }
  }
  if ("BIW" %in% count_df$Prj){ 
    count_df$date[count_df$Prj == "BIW"] <- as.character('10/01/2020')
    count_df$dateSAP[count_df$Prj == "BIW"] <- as.character('10/01/2015')
  }
  
  count_df$date <- as.Date(count_df$date, format = "%m/%d/%Y")
  count_df$dateSAP <- as.Date(count_df$dateSAP, format = "%m/%d/%Y")
  count_df <- data.frame(count_df[order(count_df$date),], row.names = NULL)
  
  plt<-ggplot(count_df, aes(date, Count, label = Prj, color = Dev, shape = Doc))+
    geom_point()+ geom_text_repel(show.legend = FALSE)+theme_classic()+
    labs(title = Title, x ="Document release date", y = "Count", color = "Developer", shape = "Document")
  pltSAP<-ggplot(count_df, aes(dateSAP, Count, label = Prj, color = Dev, shape = Doc))+
    geom_point()+ geom_text_repel(show.legend = FALSE)+theme_classic()+
    labs(title = Title, x ="SAP release date", y = "Count", color = "Developer", shape = "Document")  
  
  
  # if (!is.null(bin)){
  #   ap <- data.frame(title= Title, Cor = cor(as.numeric(count_df$date), count_df$Count), type = "#")
  #   bin<<-rbind(bin, ap)
  # }
  
  if ("BIW" %in% count_df$Prj){ 
     plt<-plt + geom_segment(aes(
       x=date[Prj == "BIW"], 
       y=Count[Prj == "BIW"], 
       xend=as.Date(-Inf), 
       yend=Count[Prj == "BIW"]),
       color = 'black',
       arrow = arrow(length=unit(0.5, 'cm')))
     pltSAP<-pltSAP + geom_segment(aes(
       x=dateSAP[Prj == "BIW"], 
       y=Count[Prj == "BIW"], 
       xend=as.Date(-Inf), 
       yend=Count[Prj == "BIW"]),
       color = 'black',
       arrow = arrow(length=unit(0.5, 'cm')))
  }
  if (mode == 'SAP'){
    return(plt)}else{
      return(pltSAP)}
}
```

Row counting as a proportion of total line items function

```{r}
RowCountsFreq <- function(OgClassData, ClassData, Title, bin = NULL) {
  lineCounts <- table(ClassData$prj)
  lineCounts <- data.frame(Prj = names(lineCounts), Count = as.vector(lineCounts))
  OglineCounts <- table(OgClassData$prj)
  OglineCounts <- data.frame(Prj = names(OglineCounts), Count = as.vector(OglineCounts))
  
  OglineCounts <- OglineCounts[OglineCounts$Prj %in% lineCounts$Prj, ]
  count_df <- data.frame(Prj = lineCounts$Prj, Count = lineCounts$Count, OgCount = OglineCounts$Count)
  count_df$freq <- (count_df$Count / count_df$OgCount) * 100
  count_df$date <- metaData$prjDate[match(count_df$Prj, metaData$prjCode)]
  count_df$Dev <- metaData$Developer[match(count_df$Prj, metaData$prjCode)]
  count_df$Doc <- metaData$DocType[match(count_df$Prj, metaData$prjCode)]
  count_df$Consult <- metaData$Consultantcy[match(count_df$Prj, metaData$prjCode)]
  prjNames <- unique(classData$prj)
 
  for (i in prjNames){
    if (!(i %in% as.vector(count_df$Prj))){
      count_df <- rbind(count_df, data.frame(Prj = i, 
                          Count = 0, 
                          OgCount =0,
                          freq = 0, 
                          date = metaData$prjDate[match(i, metaData$prjCode)], 
                          Dev = metaData$Developer[match(i, metaData$prjCode)], 
                          Doc = metaData$DocType[match(i, metaData$prjCode)],
                          Consult = metaData$Consultantcy[match(i, metaData$prjCode)]))
    }
  }
  
  if ("BIW" %in% count_df$Prj){ 
    count_df$date[count_df$Prj == "BIW"] <- as.character('10/01/2020')
  }
  
  count_df$date <- as.Date(count_df$date, format = "%m/%d/%Y")
  count_df <- data.frame(count_df[order(count_df$date),], row.names = NULL)
  
  plt<-ggplot(count_df, aes(date, freq, label = Prj, color = Dev, shape = Doc))+
    geom_point()+ geom_text_repel(show.legend = FALSE)+theme_classic()+
    labs(title = Title, x ="Document release date", y = "frequency %", color = "Developer", shape = "Document")
  
  if (!is.null(bin)){
    ap <- data.frame(title= Title, Cor = cor(as.numeric(count_df$date), count_df$freq), type = "%")
    bin<<-rbind(bin, ap)
  }
  if ("BIW" %in% count_df$Prj){ 
     plt<-plt + geom_segment(aes(
       x=date[Prj == "BIW"], 
       y=freq[Prj == "BIW"], 
       xend=as.Date(-Inf), 
       yend=freq[Prj == "BIW"]),
       color = 'black',
       arrow = arrow(length=unit(0.5, 'cm')))
  }
  return(plt)
}
```

Histogram Function:

```{r}
library(ggplot2)
RowHist <- function(ClassData, Title) {
lineCounts <- sort(table(ClassData$prj))
  
  
  
  count_df <- data.frame(Prj = names(lineCounts), Count = as.vector(lineCounts))
  count_df$date <- metaData$prjDate[match(count_df$Prj, metaData$prjCode)]
  count_df$date <- as.Date(count_df$date, format = "%m/%d/%Y")

# Create intervals using cut()
cuts <- cut(count_df$date, breaks = '3 months')
interval_labels <- as.Date(levels(cuts))

# Calculate the mean of Count within each interval
mean_values <- aggregate(Count ~ cuts, data = count_df, FUN = mean)

# Create a complete set of intervals
all_intervals <- data.frame(cuts = levels(cuts))

# Merge mean_values with all_intervals, filling missing values with 0
mean_values_complete <- merge(all_intervals, mean_values, by = "cuts", all.x = TRUE)
mean_values_complete[is.na(mean_values_complete)] <- 0

# Plot the histogram with mean values
plt<- ggplot(mean_values_complete, aes(cuts, Count)) +
  geom_histogram(stat = 'identity') +
  labs(x = "Time", y = "Count", title = Title) +
  theme_classic()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

return(plt)
}

#RowHist(classData, "Slay")

```

### Base Line Counts of All Line items

```{r}
RowCounts(classData, "Counts of all line items")
RowHist(classData, "Binned Counts of all line items")
```

Example

```{r}
RowCounts(classData[classData$Mon == TRUE, ], "Line Items for Monitoring")
RowCountsFreq(classData, classData[classData$Mon == TRUE, ], "Frequency of Line Items for Monitoring")
RowHist(classData[classData$Mon == TRUE, ], "Line Items for Monitoring")

```

Upward trajectory

# Looking at just committed to measures

We do this by sorting out all classData where the first digit in the code == 1

```{r}
#Sorting out all non committed to measures
classData_exp <- classData[classData$comit == 1, ] #use exp to not mess with original set

#run the same baseline counts
RowCounts(classData_exp, "Line Item counts of committed to measures")

RowCountsFreq(classData, classData_exp, 'Proportion of Committed to All')

RowHist(classData_exp, "Line Item counts of committed to measures")

```

# Looking at Mit/Mon on Committed Measures

```{r}
classData_exp <- classData[classData$comit == 1, ] # Only committed
classData_exp <- classData
classData_Mon <- classData_exp[classData_exp$Mon == TRUE, ]
classData_Mit <- classData_exp[classData_exp$Mit == TRUE, ]

#Comparing MON MIT over committed Measures
#Raw Couts
RowCounts(classData_Mon, "Monitoring")
RowCounts(classData_Mit, "Mitigation")

#Count frequency compared to total measures
RowCountsFreq(classData_exp, classData_Mon, "Monitoring measures as a precentage of total project line items")
RowCountsFreq(classData_exp, classData_Mit, "Mitigation measures as a precentage of total project line items")

RowHist(classData_Mon, "Monitoring")
RowHist(classData_Mit, "Mitigation")
```

# Looking At project phase on committed measures

```{r}
classData_exp <- classData[classData$comit == 1, ] # Only committed
classData_exp <- classData

classData_Pre <- classData_exp[classData_exp$PreC == TRUE, ]
classData_C <- classData_exp[classData_exp$Con == TRUE, ]
classData_OM <- classData_exp[classData_exp$OM == TRUE, ]
classData_D <- classData_exp[classData_exp$Dcom == TRUE, ]

RowCounts(classData_Pre, "Pre-Construction")
RowCounts(classData_C, "Construction")
RowCounts(classData_OM, "OM")
RowCounts(classData_D, "Decom")

# RowCountsFreq(classData_exp, classData_Pre, "PreCon measures as a precentage of total project line items")
# RowCountsFreq(classData_exp, classData_C, "Construction measures as a precentage of total project line items")
# RowCountsFreq(classData_exp, classData_OM, "OM measures as a precentage of total project line items")
# RowCountsFreq(classData_exp, classData_D, "Decom measures as a precentage of total project line items")

RowHist(classData_Pre, "Pre-Construction")
RowHist(classData_C, "Construction")
RowHist(classData_OM, "OM")
RowHist(classData_D, "Decom")
```

# Looking at Location

```{r}
loc <- c('Site', "Cable", 'OnShore')
classData_exp <- classData[classData$comit == 1, ] # Only committed
classData_exp <- classData
bin = data.frame()
gListCol <- list()
gListRow <- list()
co <- 1
for (l in loc){
  
  classData_l <- classData_exp[sapply(classData_exp$Loc, function(x) any(grepl(l, unlist(strsplit(x, ","))))), ]

  
  gListRow[[1]] <- RowCounts(classData_l, paste("Location:", l))
  gListRow[[2]] <- RowCounts(classData_l, paste("Location:", l), mode = "SAP")
  gListRow[[3]] <- RowCountsFreq(classData_exp, classData_l,paste("Frequency of Location:", l),bin )
  gListRow[[4]] <- RowHist(classData_l, paste("Location:", l))
  gListCol[[co]] <- gListRow[]
  co <- co+1
}

grid_arrangements <- list()

# Iterate through the nested lists
for (sub_list in gListCol) {
  # Use do.call to unpack the graphs in the sub-list and arrange them
  grid_arrangements[[length(grid_arrangements) + 1]] <- do.call(grid.arrange, c(sub_list, nrow = length(sub_list)))
}

# Create a final grid arrangement using the grid arrangements list
final_plot <- do.call(grid.arrange, c(grid_arrangements, ncol = length(grid_arrangements)))

# Display the final grid arrangement
ggsave("C:/Users/24chi/Desktop/OffshoreWind/images/Location_Eplore.jpeg", final_plot, height = 15, width = length(grid_arrangements)*7, limitsize = FALSE)
```

# Looking at protected resources

```{r}
knitr::opts_chunk$set(echo = T,
                      results = "hide")
recource <- c("MarineMams", "Turts", "Birds", "Bats", "Benthic", "AirQ", "WaterQ", "AcouAbove", "AcouBelow","Fish", "EssFishHabs", "CultArcheo", "CoastalHabs", "WetLands", "RecTourism", "RecComFisheries","VesselNav", "SocioEcon", "EnviroJustice", "PubHealth", "Visual", "FAA-DOD","Other")

classData_exp <- classData[classData$comit == 1, ] # Only committed
classData_exp <- classData
bin = data.frame()
gListCol <- list()
gListCol <- list()

for (r in recource) {
  classData_r <- classData_exp[sapply(classData_exp$Prot, function(x) any(grepl(r, unlist(strsplit(x, ","))))), ]
  
  gListRow <- list(
    RowCounts(classData_l, paste("Protected Resource:", r)),
    RowCounts(classData_l, paste("Protected Resource:", r), mode = "SAP"),
    RowCountsFreq(classData_exp, classData_l, paste("Frequency of Protected Resource:", r), bin),
    RowHist(classData_l, paste("Protected Resource:", r))
  )
  
  gListCol[[length(gListCol) + 1]] <- grid.arrange(grobs = gListRow, nrow = length(gListRow))
}

# Create a final grid arrangement using the grid arrangements list
final_plot <- grid.arrange(grobs = gListCol, ncol = length(gListCol))

# Save the final plot as an image
ggsave("C:/Users/24chi/Desktop/OffshoreWind/images/ProtRec_Explore.jpeg", final_plot, height = 15, width = length(gListCol) * 7, limitsize = FALSE)

# Display the final grid arrangement
```

# Ab/Bl

```{r}
AbBl <- c('AboveWater', "BelowWater")
classData_exp <- classData[classData$comit == 1, ] # Only committed
classData_exp <- classData
bin = data.frame()
for (r in AbBl){
  classData_r <- classData_exp[sapply(classData_exp$AB, function(x) any(grepl(r, unlist(strsplit(x, ","))))), ]

 RowCounts(classData_r, paste("Above/Below:", r), bin)
  
#  print(RowCountsFreq(classData_exp, classData_r,paste("Above/Below:", r, "from Committed Measures"), bin))
  
 # print(RowHist(classData_r, paste("Above/Below:", r)))

}
```

# Can you pull correlations off these things?

yes yes you can - kinda feels like psudo stats

```{r}
classData_exp <- classData
lineCounts <- sort(table(classData_exp$prj))
count_df <- data.frame(Prj = names(lineCounts), Count = as.vector(lineCounts))
count_df$date <- metaData$prjDate[match(count_df$Prj, metaData$prjCode)]
count_df$date <- as.Date(count_df$date, format = "%m/%d/%Y")
count_df <- data.frame(count_df[order(count_df$date),], row.names = NULL)

correlation <- cor(as.numeric(count_df$date), count_df$Count)
```

```{r}
#Better way to count rows

```

# Protected Resource Larger Cats

```{r}
classData_exp <- classData
bin = data.frame()

for (r in widerCatsName){
  classData_r <- classData_exp[sapply(classData_exp$widerCatsall, function(x) any(grepl(r, unlist(strsplit(x, ","))))), ]

  
  print(RowCounts(classData_r, paste("Resource Catigory:", r, "from Committed Measures"), bin))
  
  # print(RowCountsFreq(classData_exp, classData_r,paste("Frequency of Protected Resource:", r, "from Committed Measures"), bin))
  # print(RowHist(classData_r, paste("Resource Catigory:", r)))

}
```

# One to One Graphs - Above Vs Below

```{r}
AbBl <- c('AboveWater', "BelowWater")
classData_exp <- classData#[classData$comit == 1, ] # Only committed

for (r in AbBl){
  classData_r <- classData_exp[sapply(classData_exp$AB, function(x) any(grepl(r, unlist(strsplit(x, ","))))), ]
  ifelse(r == 'AboveWater', classData_Ab <- classData_r, classData_Bl <- classData_r )
}


lineCountX <- table(classData_Ab$prj)
lineCountY <- table(classData_Bl$prj)
  count_df <- data.frame(Prj = names(lineCountX), CountX = as.vector(lineCountX), CountY = as.vector(lineCountY))
  count_df$date <- metaData$prjDate[match(count_df$Prj, metaData$prjCode)]
  count_df$Dev <- metaData$Developer[match(count_df$Prj, metaData$prjCode)]
  count_df$Doc <- metaData$DocType[match(count_df$Prj, metaData$prjCode)]
  count_df$Consult <- metaData$Consultantcy[match(count_df$Prj, metaData$prjCode)]

  

  plt<-ggplot(count_df, aes(CountX, CountY, label = Prj, color = Dev, shape = Doc))+
    geom_point()+ geom_text_repel(show.legend = FALSE)+theme_classic()+
    labs(title = NULL, x ="Above Water measures", y = "Below Water measures", color = "Developer", shape = "Document")+ 
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed")

  hit <- 3
  ggsave("ABBL.png", plt, height = hit, width = hit*1.95)
  plt
  
  width <- 6
height <- width*10/16



ggsave("fig5.png", plt, height = height, width =width, dpi = 300)

```

### Mon vs Mit

```{r}
classData_exp <- classData #[classData$comit == 1, ] # Only committed

classData_Mon <- classData_exp[classData_exp$Mon == TRUE, ]
classData_Mit <- classData_exp[classData_exp$Mit == TRUE, ]


lineCountX <- table(classData_Mon$prj)
lineCountY <- table(classData_Mit$prj)
  count_df <- data.frame(Prj = names(lineCountX), CountX = as.vector(lineCountX), CountY = as.vector(lineCountY))
  count_df$date <- metaData$prjDate[match(count_df$Prj, metaData$prjCode)]
  count_df$Dev <- metaData$Developer[match(count_df$Prj, metaData$prjCode)]
  count_df$Doc <- metaData$DocType[match(count_df$Prj, metaData$prjCode)]
  count_df$Consult <- metaData$Consultantcy[match(count_df$Prj, metaData$prjCode)]

  

  plt<-ggplot(count_df, aes(CountX, CountY, label = Prj, color = Dev, shape = Doc))+
    geom_abline(slope = 5, intercept = 0, color = "red", linetype = "dashed")+
    geom_point()+ geom_text_repel(show.legend = FALSE, force = 3)+theme_classic()+
    labs(title = NULL, x ="Monitoring Measures", y = "Mitigation Measures")

  plt
  
width <- 6
height <- width*10/16



ggsave("fig4.png", plt, height = height, width =width, dpi = 300)

```

# Time Line of Vineyard Wind

```{r}
library(timevis)
library(ggplot2)

file_path <- "C:/Users/24chi/Desktop/OffshoreWind/TimeLine.xlsx"

data <- read_excel(file_path, sheet = 1) #Grabbing the data from excel
dataRef <- read_excel(file_path, sheet = 2) #Grabbing the data from excel
data$id<-c(1:nrow(data))
data$start <- as.Date(data$start)

data$group <- factor(data$group, levels = c("Coastal Virginia", "Revolution Wind",'South Fork',  "Vineyard Wind", "Ocean Wind 1", "New England Wind", "Empire Wind", "Kittyhawk", "Sunrise Wind", "Atlantic Shores South", "Mayflower / South Coast"))



data$color<-factor(data$color, levels = c("SAP","COP Submit", "NOI EIS", "DEIS Release", "FEIS Release", "ROD Release", "COP Approval", "COP Update", "COP Other", "Comment End", "Other" ))
data$size <- dataRef$Size[match(data$color, dataRef$Tags)]

matchdf <- data.frame(
  nameLong = c("Vineyard Wind", "South Fork", "Ocean Wind 1", "Revolution Wind", "Kittyhawk", "Coastal Virginia", "Sunrise Wind", "New England Wind", "Mayflower / South Coast", "Atlantic Shores South", "Empire Wind"),
  nameShort = c("YVW", "SFR", "OWO", "REV", "KHW", 'CVW', "SUN", "NEW", "MFW", "ASS", "EPW"))

data$prj <- matchdf$nameShort[match(data$group, matchdf$nameLong)]
data$dev <- metaData$Developer[match(data$prj, metaData$prjCode)]

library(randomcoloR)


category_colors <- c(
'SAP' = "#42d4f4",#
'COP Submit' = "#3cb44b",#
'COP Other' = "#aaffc3",
'DEIS Release' = "#800000",#
'Comment End' = "#a9a9a9",
'NOI EIS' = "#dcbeff",#
'COP Approval' = "#ffe119",#
'ROD Release' = "#f58231",#
'FEIS Release' = "#e6194B",#
'COP Update' = "#bfef45",
'Other' = "#000000"
)

devList <- unique(data$dev)
colors<- generate_colors <- function(n) {
  colors <- randomColor(n, luminosity = "bright")
  return(colors)
}
colors <- generate_colors(length(devList))



plt<-ggplot(data, aes(start, group, color = color, size = size))+
  geom_point()+
  scale_size(guide = "none") +
  scale_color_manual(values = category_colors) +
  theme_linedraw()+
  geom_vline(xintercept = as.Date("2023-07-18"), linetype = "dashed", color = "black")+
  labs(title = "", x = '', y='', color = "")

ggsave("TimeLine.png", plt, height = 4.5, width = 10, bg = "transparent")
plt
#vistime(data, linewidth = 10)
```

```{r}
install.packages("vistime")
library(vistime)


```

# Playing around with the Data

```{r}
library(tidyr)
classData_exp <- classData

recource <- c("MarineMams", "Turts", "Birds", "Bats", "Benthic", "AirQ", "WaterQ", "AcouAbove", "AcouBelow","Fish", "EssFishHabs", "CultArcheo", "CoastalHabs", "WetLands", "RecTourism", "RecComFisheries","VesselNav", "SocioEcon", "EnviroJustice", "PubHealth", "Visual", "FAA-DOD","Other")

data_sep_tags <- classData_exp %>%
  separate_rows(Prot, sep = ", ")

# Step 2: Group the data by project and tag, and then count the occurrences
tag_counts <- data_sep_tags %>%
  group_by(prj, Prot) %>%
  summarize(count = n())

fullCount <- data_sep_tags %>%
  group_by(prj) %>%
  summarize(count = n())

all_combinations <- expand.grid(
  prj = unique(tag_counts$prj),
  Prot = recource
)

tagCounts <- all_combinations %>%
  left_join(tag_counts, by = c("prj", "Prot")) %>%
  replace_na(list(count = 0))

tagCounts$prec <- tagCounts$count / fullCount$count[match(tagCounts$prj, fullCount$prj)]

Rank <- tagCounts %>%
  group_by(Prot) %>%
  summarize(count = mean(prec))

tagCounts$Prot <- factor(tagCounts$Prot, levels = first( list(Rank$Prot[order(Rank$count)])   ))
# tagCounts$prj <- factor(tagCounts$prj, levels = c("BIW", "YVW", "SFR", "OWO", "REV", "KHW", 'CVW', "SUN", "NEW", "MFW", "ASS", "EPW"))
tagCounts$prj <- factor(tagCounts$prj, levels = c('BIW','CVW', "REV", "SFR", "YVW", "OWO", "NEW", "EPW", "KHW", "SUN", "ASS", "MFW")
)

plt <- ggplot(tagCounts, aes(prj, Prot, size = prec, color = prec))+
  scale_color_gradient(low = "blue", high = "red") +
  labs(title = NULL,x=NULL, y=NULL, color = 'Freq\nof Tag')+
  geom_point()+  guides(size = 'none')+
  theme_minimal()+
  theme(legend.position ='bottom', axis.text.x = element_text(angle = 90, hjust = 1))

wid <- 3.5
ggsave("CountbyProt.png", plt, width = wid, height = wid*1.4)
plt

library(cowplot)
leg <- get_legend(plt)
print(leg)
# Extract the legend from the grob

# Print the extracted legend

ggplot(tagCounts, aes(prj, prec))+geom_bar(stat = 'identity')+facet_wrap(tagCounts$Prot, ncol=1)

width <- 6
height <- width*10/12



ggsave("fig3.png", plt, height = width, width =height, dpi = 300)

```

## hh

/

```{r}
1+1
```
